Draft Exploration

### 2020-04-19 draft_exploration.Rmd
made war and career length into functions

hs_mlb_war <- master %>%
  filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
  filter(mlb_end <= 2017) %>%
  group_by(signed) %>%
  summarize(q1 = quantile(war, 0.25),
            median_war = median(war),
            mean_war = mean(war),
            q3 = quantile(war, 0.75))

@@

hs_mlb_inactive <- master %>%
  filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
  filter(mlb_end <= 2017)

ggplot(hs_mlb_inactive, aes(signed, war/mlb_length, fill = signed)) +
  geom_boxplot() +
  coord_flip() +
  theme_light() +
  labs(
    x = "Career MLB Wins Above Replacement",
    y = "Signed out of High School?",
    title = "MLB Career Wins Above Replacement of High School Picks to Reach MLB",
    subtitle = "Grouped by whether player signed out of high school"
  )

>>>>

career_length <- function(pos = c("C", "1B", "2B", "3B", "SS", "OF", "P")) {

  hs_mlb_inactive <- master %>%
    filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
    filter(position %in% pos) %>%
    filter(mlb_end <= 2017)

career_length()
```

war_summary <- function(pos = c("C", "1B", "2B", "3B", "SS", "OF", "P")) {

  hs_mlb_war <- master %>%
    filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
    filter(position %in% pos) %>%
    filter(mlb_end <= 2017) %>%
    group_by(signed) %>%
    summarize(q1 = quantile(war, 0.25),
              median_war = median(war),
              mean_war = mean(war),
              q3 = quantile(war, 0.75))

@@

war_summary()
```
